Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-29 paper/paper7/paper7.tex
evaluation

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
In close collaboration with several \emph{SBE} domain experts, we defined 246 constraint 
of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level. 
For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
We distinct two classes of vocabularies: 
(1) established vocabularies (e.g., \emph{QB}, \emph{SKOS}) which are widely adopted and accepted and 
(2) newly developed vocabularies (e.g., \emph{Disco} which will be published in 2015) which are either recently published or are still in the publication process.
It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
and that early adopters did not properly understand its formal specification.
Based on this evaluation we formulate hypotheses.
Nevertheless, we have to be careful making general statements for all vocabularies 
as these hypotheses still have to be verified or falsified in terms of future work 
by evaluating the quality of data represented by additional established and newly developed vocabularies.

@@

\begin{hyp}
Complex constraints are met by data represented by established vocabularies but not by data represented by newly developed vocabularies. 
\end{hyp}
It is likely that a newly developed vocabulary is still subject of constant change, that published data may not be consistent with its current version,
and that early adopters did not properly understand its formal specification.

>>>>

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
In close collaboration with several \emph{SBE} domain experts, we defined 246 constraint 
of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level. 
For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
We distinct two classes of vocabularies: 
(1) established vocabularies (e.g., \emph{QB}, \emph{SKOS}) which are widely adopted and accepted and 
(2) newly developed vocabularies (e.g., \emph{Disco} which will be published in 2015) which are either recently published or are still in the publication process.
%It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
%and that early adopters did not properly understand its formal specification.
Based on this evaluation we formulate hypotheses.
Nevertheless, we have to be careful making general statements for all vocabularies 
as these hypotheses still have to be verified or falsified in terms of future work 
by evaluating the quality of data represented by additional established and newly developed vocabularies.

@@

It is likely that a newly developed vocabulary is still subject of constant change, 
that published data may not be consistent with its current version,
and that early adopters did not properly understand its formal specification.

\begin{hyp}
Complex constraints are met by data represented by established vocabularies but not by data represented by newly developed vocabularies. 
\end{hyp}
